\documentclass[final,3p,times,11pt]{elsarticle}
\usepackage[USenglish]{babel}
\usepackage{amsmath,amssymb,amsthm, mathrsfs,multirow}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{stmaryrd}
\usepackage[dvipsnames]{xcolor}
\usepackage{cancel}
\usepackage{ulem}
\usepackage{tabularx}
\usepackage{comment}
%\usepackage{subcaption}
%\usepackage[show]{ed}
%\usepackage{showkeys}
%\usepackage{showlabels}
%\usepackage[notcite,notref]{showkeys}
%\usepackage{refcheck}
% \usepackage[ruled,vlined]{algorithm2e}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\definecolor{Myblue}{rgb}{.2 0.4 1}

\usepackage{hyperref}
\hypersetup{
    %bookmarks=true,         % show bookmarks bar?
    colorlinks = true,       % false: boxed links; true: colored links
    % linkcolor=green
     %linkcolor=red,          % color of internal links (change box color with linkbordercolor)
     %citecolor=green,        % color of links to bibliography
    %filecolor=magenta,      % color of file links
    %urlcolor=cyan           % color of external links
}
%\usepackage{wrapfig}
%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%\usepackage{lineno}


% ==============   Macros  ====================
\newcommand{\mynabla}{\widetilde{\nabla}} 
\newcommand{\jump}[1]{[\![#1]\!]}
\newcommand{\HEcolor}[1]{{\textcolor{blue}{#1}}}
\newcommand{\TSVcolor}[1]{{\textcolor{orange}{#1}}}
\newcommand{\JLcolor}[1]{{\textcolor{violet}{#1}}} %violet
\newcommand{\Grids}{\boldsymbol{\chi}}

\newtheorem{theorem}{Theorem}%[section]
\newtheorem{lemma}{Lemma}%[section]
\newtheorem{VariationalForm}[theorem]{Variational Formulation}
% =============================================

\journal{}
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{}%
 \let\@evenfoot\@oddfoot}
\makeatother




\begin{document}
\begin{frontmatter}
\title{Estimation of model correlations for multi-fidelity Monte Carlo for uncertainty quantification}


\author[umdcs]{Matthias Heinkenschloss}
\ead{heinken@rice.edu}
\address[umdcs]{Department of Computational Applied Mathematics and Operations Research and the Ken Kennedy Institute, Rice University.}
\author[umdm]{Jiaxing Liang}
\ead{jl508@rice.edu}
\address[umdm]{Department of Computational Applied Mathematics and Operations Research, Rice University.}
% \author[UA]{Tonatiuh S\'anchez-Vizuet}
% \ead{tonatiuh@arizona.edu}
% \address[UA]{Department of Mathematics, The University of Arizona.}
\begin{abstract}
We present an adaptive parameter estimation methodology to address the challenge of unknown model correlation coefficients in the multi-fidelity Monte Carlo framework for efficient uncertainty quantification in the presence of parametric variability. In practical applications for multi-fidelity Monte Carlo, key parameters such as model correlation coefficients are typically unknown and must be estimated from sample statistics. We address this challenge by deriving sensitivity bounds and confidence intervals for correlation coefficient estimators, which inform a sequential pilot sampling strategy with rigorous stopping criteria. This enables dynamic calibration of the multi-fidelity Monte Carlo estimators while ensuring controlled error propagation from parameter estimation to overall accuracy and cost. The resulting algorithm adaptively identifies the minimal pilot sample size required for reliable performance, avoiding unnecessary computational expense. Numerical experiments confirm the effectiveness of the proposed approach in delivering accurate statistical estimates with significantly fewer high-fidelity evaluations than standard Monte Carlo. This framework substantially improves the practicality and efficiency of MFMC in realistic scenarios.
\end{abstract}

\begin{keyword}
Multi-fidelity Monte Carlo Finite-Element \sep Parameter estimation for correlation coefficient\sep Parametric expectation \sep Uncertainty quantification
%
\MSC[2020] 
\end{keyword}
\end{frontmatter}

\input{./Sections/Introduction} 
\input{./Sections/Physical_Problem} 
% \input{./Sections/Sparse_Grid_Stochastic_Collocation}
\input{./Sections/MC}
\input{./Sections/MFMC}
\input{./Sections/Parameter_Estimation}
\input{./Sections/Interval_parameter_estimation}
\input{./Sections/Numerical_result}
\input{./Sections/Acknowledgment}
\input{./Sections/Appendix}


\bibliographystyle{abbrv}
% \bibliographystyle{alphaurl}
\bibliography{references_liang}
\end{document}