\documentclass[final,3p,times,11pt]{elsarticle}
\usepackage[USenglish]{babel}
\usepackage{amsmath,amssymb,amsthm, mathrsfs,multirow}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{stmaryrd}
\usepackage[dvipsnames]{xcolor}
\usepackage{cancel}
\usepackage{ulem}
\usepackage{tabularx}
\usepackage{comment}
%\usepackage{subcaption}
%\usepackage[show]{ed}
%\usepackage{showkeys}
%\usepackage{showlabels}
%\usepackage[notcite,notref]{showkeys}
%\usepackage{refcheck}
% \usepackage[ruled,vlined]{algorithm2e}
\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\definecolor{Myblue}{rgb}{.2 0.4 1}

\usepackage{hyperref}
\hypersetup{
    %bookmarks=true,         % show bookmarks bar?
    colorlinks = true,       % false: boxed links; true: colored links
}



% ==============   Macros  ====================
\newcommand{\real}{\mathbb{R}} 
\newcommand{\nat}{\mathbb{N}} 


\newcommand{\mynabla}{\widetilde{\nabla}} 
\newcommand{\jump}[1]{[\![#1]\!]}
\newcommand{\HEcolor}[1]{{\textcolor{blue}{#1}}}
\newcommand{\TSVcolor}[1]{{\textcolor{orange}{#1}}}
\newcommand{\JLcolor}[1]{{\textcolor{violet}{#1}}} %violet
\newcommand{\Grids}{\boldsymbol{\chi}}

\newtheorem{theorem}{Theorem}%[section]
\newtheorem{lemma}{Lemma}%[section]
\newtheorem{VariationalForm}[theorem]{Variational Formulation}
% =============================================

\journal{}
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{}%
 \let\@evenfoot\@oddfoot}
\makeatother




\begin{document}
\begin{frontmatter}
\title{Iterative estimation of integer sample size for multi-fidelity Monte Carlo\tnoteref{t1}}
\tnotetext[t1]{This research was supported in part by AFOSR Grant FA9550-22-1-0004 and NSF Grant DMS-2231482.}



% \author[RiceCMOR]{Damon Spencer}
% \ead{heinken@rice.edu}
% \address[RiceCMOR]{Department of Computational Applied Mathematics \& Operations Research, Rice University.}
\author[MH]{Matthias Heinkenschloss}
\ead{heinken@rice.edu}
\address[MH]{Department of Computational Applied Mathematics \& Operations Research and The Ken Kennedy Institute, Rice  University.}
\author[JL]{Jiaxing Liang}
\ead{jl508@rice.edu}
\address[JL]{Department of Computational Applied Mathematics \& Operations Research, Rice University.}

\begin{abstract}
Optimal sample allocation in multifidelity Monte Carlo (MFMC) methods is conventionally obtained from a continuous relaxation of the allocation problem, followed by rounding to enforce integer sample sizes. However, such post hoc rounding often leads to budget under-utilization and diminished variance reduction efficiency. This paper presents a novel iterative allocation scheme that computes integer-valued sample sizes directly within a recursive optimization framework. The proposed method preserves the analytical structure of the continuous optimum while ensuring strict adherence to budget constraints and maintaining monotonicity across fidelity levels. Theoretical analysis establishes improved variance and cost bounds compared to direct rounding strategies, and numerical experiments confirm enhanced estimator accuracy and budget utilization. The results demonstrate that the proposed scheme provides a robust and practical framework for optimal sample allocation in multifidelity Monte Carlo estimation.
\end{abstract}





\begin{keyword}
Multi-fidelity Monte Carlo \sep Sample Allocation \sep Integer Optimization  \sep Uncertainty Quantification \sep Variance Reduction.
%
\MSC[2020] 65C05\sep 62K05 \sep 49M20.
\end{keyword}
\end{frontmatter}

\input{./Sections/Introduction} 
\input{./Sections/MFMC} 
\input{./Sections/MFMC_Nk_optimization}
\input{./Sections/Iterative_Integer_Valued_Sample_Size}
\input{./Sections/Modified_iterative_Integer_Valued_Sample_Size}
\input{./Sections/Numerics} 
\input{./Sections/Conclusion} 
% \input{./Sections/Illustration}


\bibliographystyle{abbrv}
% \bibliographystyle{alphaurl}
\bibliography{references_liang}
% \bibliography{reference}
\end{document}


